Zero-Knowledge Credentials for Smart Contracts

### 2018-05-13 paper/paper.tex
Stuff

\subsection{Prior Work}
A generalized scheme was proposed by \citet{garmanDecentralizedAnonymousCredentials2013}

\section{Properties and Features}

@@

\subsection{Credential Scheme}

>>>>

\subsection{Prior Work}
Identity systems for public blockchains have been proposed before in the form of
serivces like Civic and Uport, wherein users can acquire attestations from
trusted issuers about facets of their identity (name, age, country of origin,
etc). These services promise ``anonymous'' attestation, but are
\textit{linkable}, i.e.\ multiple attestations by the same user are trivially
identifiable, and \textit{pseudonymous}, i.e.\ attestations are
linked to a pseudonym that is known by the credential issuer. If a credential
issuer leaks their records, then all past activity by a user is deanonymized.

A zero-knowledge credential scheme for blockchains was proposed by
\citet{garmanDecentralizedAnonymousCredentials2013}, using zkSNARKS. Our system
adapts this scheme for the Ethereum\cite{woodEthereumSecureDecentralised2014} blockchain and implements more expressive
forms of credentials that can be easily utilized for ad-hoc attestations in zero-knowledge.

\subsection{Protocol Overview}
\subsubsection{Actors}
The major actors in this protocol are \textit{issuers}, \textit{verifiers} and
\textit{users}. A verifier is a  smart-contract that wants to ensure that
users calling a function are authorized to do so. In order to authorize users,
the contract designates an issuer, who is responsible for granting credentials
to users and keeping a Merkle tree of valid credentials. The verifier then
requires that each user provide a zero-knowledge proof that the user possesses a
credential in the merkle tree with attributes in the required range. Both
credential issuance and usage is done in zero-knowledge and attestations are
reusable and unlinkable.

\subsection{Implementation}
We implement zero-knowledge proofs using the elliptic curve pairing precompiled
contracts in Ethereum, using the Pinnochio protocol
\cite{parnoPinocchioNearlyPractical2013}. We constructed the arithmetic circuits
for the proofs using libsnark \cite{ben-sassonSNARKsVerifyingProgram2013}.
Commitment trees are stored using IPFS \cite{benetIPFSContentAddressed2014}.

\section{Properties and Features}
Our zero-knowledge identity system allows for highly flexible ad-hoc issuance of
credentials through \textit{k-show} credentials and range-bounded attributes.

The public inputs are
\begin{equation*}
  \texttt{m\_root},\ \{l_1, \dots, l_7\},\ \{u_1, \dots, u_7\}, S, k
\end{equation*}

Each proof is an assertion that the prover holds a credential
\begin{equation*}
c = (sk, \{attr_1, \dots, attr_7\})  
\end{equation*}
 such that

\begin{enumerate}[1.]
\item The credential is a leaf of a merkle tree with root \texttt{m\_root}.
\item The credential contains some attributes $\{attr_1, \dots, attr_7\}$ with
  $attr_i \in [l_i,u_i]$
\item The credential has been used fewer than $k$ times with the salt $S$
\end{enumerate}

@@

\subsection{Credentials}
Each credential is of the form
\begin{equation*}
c =  ( \texttt{sk}, \{attr_1, \dots, attr_n\})
\end{equation*}

where $\texttt{sk} \in \{0, 1\}^\lambda$ and $attr_i \in \Z_{2^{32}}$.

\subsection{Credential Requests}
A credential request is a tuple of the form
\begin{equation*}
  r = (\texttt{merkle\_root}, \texttt{serial}, \{u_1, \dots,u_n\}, \{\ell_1,\dots,\ell_n\}, S, k)
\end{equation*}

where $\texttt{merkle\_root}$ is the root of a Merkle-tree of valid credential
commitments, $u_i, \ell_i \in \Z_{2^{32}}$ are bounds on acceptable attribute
values, $S$ is a request-specific salt, and $k\in \N$ is the allowed number of
uses of a single credential per salt $S$.

\subsection{k-show Credentials}
Every proof $\pi$ that a user generates has as public input
$\texttt{serial}_\pi$ which is defined as
\begin{equation*}
  H(\texttt{sk}_u || S_v || k)
\end{equation*}

and a public input $\texttt{k\_bound}$ such that $k\leq \texttt{k\_bound}$. For
each proof that the verifier accepts, the verifier adds $\texttt{serial}_\pi$ to
its nullifier set $N$. A verifier accepts $\pi$ only if $\pi \notin N$. Thus,
for a given salt $S_v$ the user may produce up to $\texttt{k\_bound}$ distinct
valid proofs, while remaining unlinkable. The verifier $v$ may select $S$ such
that it changes over time, for instance such that it contains the hash of the
most recent block with height a multiple of 1 million, which allows for
rate-limited credentials.

\subsection{Bounded-attributes}
A proof for a given credential request $r$ must assert that $attr_i \in [\ell_i,
u_i]$ for all $1\leq i\leq n$. This allows attestations such as ``I possess over
\$1 million'', ``I am between the ages of 21 and 45'', or ``I live in the USA'',
without revealing any additional information.

\subsection{Credential Scheme}
verifier
